Towards a Mechanized Proof of Noninterference

### 2013-12-19 paper/paper.tex

Figure~\ref{fig:value_types} includes typing judgements for values in the
language, which are mostly straight forward with the exception of
\textsc{V-Bracket}, which we discuss below along with the type rules for
expressions.

@@

Before discussing the task of mechanizing a noninterference proof for \langName,
it is useful to first view what the natural language proof would look like
first.  We first start by proving some supporting lemmas about the language's
semantics and type system, and finish with a proof of noninterference for the
language.  Since \langName is a stripped down version of \origLang, the proofs
will look like a simplified version of the proofs found in Pottier and Simonet's
paper~\cite{InfoFlowML}.

@@

  \begin{case}[$e = \textsf{ if } v \: e_1 \: e_2$ or $e =
    \textsf{ let } x := v \textsf{ in } e$]
    These are similar to the previous case.  The value $v$ can not be an integer
    and so the lifted version of $v$ can not be an integer, meaning the lifted
    expression is also stuck.
  \end{case}

>>>>

Figure~\ref{fig:value_types} includes typing judgements for values in the
language, which are mostly straightforward with the exception of
\textsc{V-Bracket}, which we discuss below along with the type rules for
expressions.

@@

Before discussing the task of mechanizing a noninterference proof for \langName,
it is useful to first view the natural language proof.  We first start by proving some supporting lemmas about the language's
semantics and type system, and finish with a proof of noninterference for the
language.  Since \langName is a stripped down version of \origLang, the proofs
will look like a simplified version of the proofs found in Pottier and Simonet's
paper~\cite{InfoFlowML}.

@@

  \begin{case}[$e = \textsf{ if } v \: e_1 \: e_2$ or $e =
    \textsf{ let } x := v \textsf{ in } e$]
    If $e$ is stuck and is an If-statement, then none of \ref{eq:lift-if}, \ref{eq:if-true}, and \ref{eq:if-false} applies. This means that $v$ can neither
    be an integer or some bracketed value.  As a result, $\lift{v}_i$ cannot
    be an integer, and so is stuck.
  \end{case}
